### 2016-01-11 pdocs/thesis/introduction.tex
pdocs

\begin{itemize}
\item \bullet - \cite{\bullet} which is used e.g. in Blender and Erwin Coumans
 has received Tehnical Academic Award for creation of the Bullet physics library, \cite{erwin.oscar}
\item Box2D - \cite\{box2d} which is used e.g. in Angry Birds
\item RigsOfRods - \cite{ror} which uses large amount of rod elements to simulate deformation and breaking of vehicles
\end{itemize}

@@

Main requirements for software implementation can be summarized
\begin{itemize}
\item solution can be integrated easily to existing dynamics engines
\item additional calculation time for each timestep may not exceed few milliseconds 
\end{itemize}

@@

Target of this work is to find out suitable methods for handling of plasticity and verify them 
in commonly used physics engine \bullet, \cite{bulletphysics}. 
Handling of plasticity basically means that objects involved may absorb kinetic energy and break.

@@

Possibility to provide simulated demostrations and verifications of new theories or exercises  would be targeted for 
studies of mechanics and strength of material. Implementation of computer programs could be done as part of computer graphics.

Methods presented in this work can be used in gaming industry to provide objects that behave more realistically than currently without significant extra work.

>>>>

\begin{itemize}
\item \bullet - \cite{bullet} which is used e.g. in Blender and Erwin Coumans
 has received Tehnical Academic Award for creation of the Bullet physics library, \cite{erwin.oscar}
\item Box2D - \cite{box2d} which is used e.g. in Angry Birds
\item RigsOfRods - \cite{ror} which uses large amount of rod elements to simulate deformation and breaking of vehicles
\end{itemize}

@@

Main requirements for software implementation can be summarized
\begin{itemize}
\item plastic deformation takes place if force or moment exceeds given limit
\item plastic deformation absorbs enegry
\item after predefined limit of displacement is exceeded constraint is deactivated 
\item results should be in same magnitude as theoretical and test results
\item solution can be integrated to existing dynamics engines
\item additional calculation time for each timestep may not exceed few milliseconds 
\end{itemize}

@@

Target of this work is to find out suitable methods for handling of plasticity and verify them 
in commonly used physics engine \bullet. 
Handling of plasticity basically means that objects involved may absorb kinetic energy and break.

@@

Possibility to provide simulated demostrations and verifications of new theories or exercises  would be targeted for 
studies of mechanics and strength of material.

Methods presented in this work can be used in gaming industry to provide objects that behave more realistically than currently without significant extra work. Efficient simulation algorithms can also help in saving energy. Saving even few wats or percent for single user makes big difference as gaming PCs are estimated to have consumed 75 TWh/year of electricity globally in 2012, \cite{gaming.energy}.
